Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-25 paper/ms.tex
update manuscript

Over the first 100 million years of their lives, exoplanet
systems are expected to undergo major physical and dynamical changes.
For a typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the disk
disperses \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant
changes over the next $\sim$10-100 million years through giant impacts
\citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal
during Earth's first 100 million years
\citep{cameron_origin_1976,canup_origin_2001}.

A number of other processes are thought to shape young exoplanets.
Planets with gaseous envelopes are expected to shrink as they
contract, and as their atmospheres undergo photoevaporation
\citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
relative importance of these two processes is set by the planetary
mass, as well as the radiation environment.  Photoevaporation in
particular can be directly observed in {\it e.g.}, the He 10830\AA\
line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in
the semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change due to viscous coupling (CITE).
High-eccentricity migration processes including planet-planet
scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
(CITE) can also occur.  The circularization timescale is thought to be
such that for any giant planets that migrated early, their orbits
should circularize within 100 million years (CITE).

@@

The transits of \pn\ are grazing, which is a cause for concern.
Particularly for a target near the galactic plane ($b=-5.8^\circ$),
background eclipsing binaries are a major source of astrophysical
false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
follow-up data show that this and related scenarios are unlikely to
the degree that we can ``validate'' the planet, {\it i.e.}, rule that
its probability of being an astrophysical false positive is negligibly
small.  We considered this effort worthwhile because of the planet's
youth.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$, scaled such that
    brighter stars are larger. The \texttt{X} and \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale. The circles show
    apertures of radii 1, 1.5, and 2.25 pixels used in our blend
    analysis (Section~\ref{subsec:validation}).  Two stars of interest
    are ``Star A'' and ``Star B'', which were eventually excluded as
    being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
    {\bf SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments.} Star A ($\Delta T=4.7$,
    $\rho=2.3$'' west) is detected in the autocorrelation function, in
    addition to being a resolved Gaia source.  It is co-moving with
    \tn, and its parallax and on-sky position imply that it is
    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:soar}
	}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		Each constraint is described in Section~\ref{subsec:fp_constraints}.
		\label{fig:fpscenario}
	}
\end{figure*}

>>>>

Over the first 100 million years of their lives, exoplanet systems are
expected to undergo major physical and dynamical changes.  For a
typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the end of disk
dispersal \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant
changes over the next $\sim$10-100 million years through giant impacts
\citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal during Earth's
first 100 million years \citep{cameron_origin_1976,canup_origin_2001}.

A number of other processes are expected to shape young exoplanets.
Planets with gaseous envelopes are thought to shrink as they contract
and as their atmospheres undergo photoevaporation \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
relative importance of contraction and photoevaporation is set by the
planetary mass, as well as the radiation environment.  The
effectiveness of photoevaporation can be inferred from observations of
planetary winds in the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

Beyond physical changes, dynamical changes are expected in the semi-major axes,
eccentricities, and stellar obliquities of young planets.  When the gas disk is
present, the planetary semi-major axis is thought to change in step with the
viscous evolution of the disk \citep{lin_orbital_1996}.  High-eccentricity
migration processes including planet-planet scattering, secular chaos, and
Kozai-Lidov oscillations can also occur \citep[{\it
e.g.},][]{chatterjee_dynamical_2008,lithwick_secular_2014,fabrycky_shrinking_2007}.
The circularization timescale is thought to be such that for any giant planets
that migrated early, their orbits should circularize within 100 million years
\citep{zahn_tidal_1977}.

@@

The transits of \pn\ are grazing, which is a cause for concern.
Particularly for a target near the galactic plane ($b=-5.8^\circ$),
background eclipsing binaries are a major source of astrophysical
false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
follow-up data show that this and related scenarios are unlikely to
the degree that we can ``validate'' the planet, {\it i.e.}, rule that
its probability of being an astrophysical false positive is negligibly
small.  We considered this result worth reporting because of the planet's
youth.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$ (brighter stars
    are larger). The \texttt{X} and \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale.  Two stars of
    interest are ``Star A'' and ``Star B'', which were eventually
    excluded as being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
    {\bf SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments.} Star A ($\Delta T=4.7$,
    $2.3''$ west) is detected in the autocorrelation function, in
    addition to being a resolved Gaia source.  It is co-moving with
    \tn, and its parallax and on-sky position imply that it is
    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:soar}
	}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
    {\it Top}: for bound companions (EB and HEB scenarios),
		{\it Bottom}: for unassociated companions along the same line of
    sight (BEB scenarios).
		Each constraint is described in Section~\ref{subsec:fp_constraints}.
		\label{fig:fpscenario}
	}
\end{figure*}
